\documentclass{article}

\title{Ashti Web Server Write-up}
\author{Elliott Lefler}

\begin{document}

\maketitle

\section{Introduction}

In this write-up, I will describe my experience working on the Ashti Web Server project.

\section*{Challenges}

During the development of the web server, I encountered several challenges. Here are three of the main challenges I faced:

\subsection*{Challenge 1}

Understanding the requirements and relaxation of HTTP 1.1 protocol for the server implementation.

\subsection*{Challenge 2}

Handling GET requests and serving the appropriate files from the disk to the web browser.

\subsection*{Challenge 3}

Implementing support for various HTTP response codes, including 200, 400, 404, and 500.

\section*{Lessons Learned}

Throughout the project, I learned important lessons that will benefit my future endeavors. Here are two of the main lessons I took away from this experience:

\subsection*{Lesson 1}

Writing modular and reusable code is crucial for efficient development and maintenance.


\subsection*{Lesson 2}

Thorough testing and handling of various edge cases, such as slow clients and error outputs from CGI scripts.

\section*{Conclusion}

In conclusion, the Ashti Web Server project was a challenging yet rewarding experience. I successfully implemented a simplified version of a web server that served files from the disk to web browsers. I gained valuable knowledge in handling HTTP requests and responses, supporting different content types, and interacting with CGI scripts. I look forward to applying these lessons in future projects and further refining the Ashti Web Server.

\end{document}
